\ifVOLONE
\item[1.] It only rains when you don't have an umbrella with you, so you can never count on the weather forecast.
\item[2.] It's cold again today, though not as cold as yesterday.
\item[3.] If I said that I'll do it, I'll see it through to the end.
\item[4.] It's locked, so they've probably gone out somewhere.
\item[5.] The weather is cloudy and grey, threatening to rain at any moment.
\item[6.] I can't figure it out at all. (I have no idea what's what.)
\item[7.] I looked out of the window for some reason or another and noticed that the leaves have turned red.
\item[8.] We are into late autumn, and the early mornings and evenings are quite chilly. How are you?
\item[9.] I read it after a fashion, but I didn't really understand what it was about.
\item[10.] Although he really knew, he pretended not to and told me nothing.
\item[11.] No matter how rapid the current is, the fish swim upstream.
\item[12.] She worked every day, without missing even a single day.
\item[13.] After you've arrived there safely, please give me a call right away.
\item[14.] Even though they say it's already spring, it's as cold as if winter were still here.
\item[15.] I have a slight headache, but since I have an exam today I have no choice but to go to school.
\item[16.] If you see Tanaka-san tomorrow, please tell him/her to give me a call.
\item[17.] One more failure and we will probably be compelled to call off the study.
\item[18.] No matter how much you eat, you don't necessarily gain weight.
\item[19.] The higher you climb on a mountain, the thinner the air becomes.
\item[20.] If I had to make a choice, I'd say that I like fish better than meat.
\item[21.] I looked over all the grammars I could lay my hands on, but no such thing appears anywhere in them.
\item[22.] After I conducted one study after another, the experiment finally yielded results.
\item[23.] Sunlight, water, and carbon dioxide are necessary for plants to grow.
\item[24.] I still can't get out of that childhood habit.
\item[25.] If I have to buy [something] regardless, I'd like to buy something that's cheap and good.
\item[26.] With this kind of academic record, you couldn't possibly get into a good university.
\item[27.] It's only natural for human beings to make mistakes.
\item[28.] People say there are too few parks in Japan, but is that really true?
\item[29.] This time very few people came, but we hope to have as many as possible next time.
\item[30.] Much to our regret, we are obliged to conclude that he is the criminal.
\item[31.] It is not until we have time to rest that we can lead our lives as human beings.
\item[32.] It's pointless to take the trouble to come to Japan and then not study Japanese.
\item[33.] I start to feel like travelling somewhere, though I don't have any particular place in mind.
\item[34.] On all the trains on the Tohoku line, skiers are packed in like sardines.(All the trains on the Tohoku line are jam-packed with skiers.)
\item[35.] I don't care who laughs at me.
\item[36.] Far from feeling relieved, I'm so worried that I can't sleep a wink at night.
\item[37.] It's been raining continuously since the day before yesterday.
\item[38.] On serene autumn nights, thoughts of my late mother come to mind.
\item[39.] The door, which should have been closed, is/was open.
\item[40.] It is rare to see such an interesting film.
\item[41.] Men are expected not just to be strong; men can't be men without gentleness.(=Real men can't just be strong; real men need to be gentle.)
\item[42.] I am told that that animal's body temperature rises along with an increase in the air temperature.
\item[43.] In the beginning it was easy, but gradually it has gotten more difficult.
\item[44.] There are just four of us here, so let's play mahjong.(=There are four of us here, which is just right for a game of mahjong.)
\item[45.] When you go to the post office, please stop by the supermarket and do the shopping.
\item[46.] The more you look at this picture, the more you can relish it(=the more interesting/pleasing it is to look at).
\item[47.] Customers are requested to note that tomorrow is our regular shop-holiday, so we will be closed.
\item[48.] I want to contact him straightaway, but unfortunately I don't have his phone number.
\item[49.] He always tells funny stories and makes us laugh.
\item[50.] A lot of trees burned down in the forest fire.
\item[51.] As long as we had water, we could survive for a few days.
\item[52.] No matter how hard it is, you must keep on trying right to the end.
\item[53.] The accident doesn't seem serious.
\item[54.] I'd like to show my appreciation to you with this little gift.
\item[55.] Although I thought it was a little expensive, I took the plunge and decided to buy it.
\item[56.] His attitude changed as suddenly as if he'd done a complete about-face.
\item[57.] People are queueing up and waiting to buy tickets.
\item[58.] The talk the teacher gave us yesterday attracted my interest.
\item[59.] The book I thought I'd lost turned up under the desk.
\item[60.] That's a bargain I found in a shop which I just happened to be passing by.
\item[61.] I inadvertently left my bag on the train.
\item[62.] The sight of the terrible traffic accident sent a chill down my spine.
\item[63.] In Taiwan, people wash their faces with cold water even in the winter.
\item[64.] Their children are already out on their own, so that couple lives quietly and comfortably.
\item[65.] We'd be very pleased to have you with us.
\item[66.] I cut my hand with a knife and it's covered with blood.
\item[67.] Fresh bread is very delicious.
\item[68.] You can't take the day off work just because it's going to rain.
\item[69.] In December, music associated with Christmas (=Christmas music) plays in town.
\item[70.] Although I know I shouldn't drink, I start having a good time and then I drink in spite of myself.
\item[71.] It appears unlikely to rain tomorrow because the sunset is [so] beautiful.
\item[72.] ``Where does your back itch?  Here?'' ``Yes, yes, there. Oh, that feels good!''
\item[73.] The relationship between language and culture is too strong to break.
\item[74.] We won't get anywhere asking every person for his/her opinion, so let's take a vote.
\item[75.] ``The strong win out in the end, don't they.'' ``Yes, such is life.''
\item[76.] Even though I said I didn't want to, I was forced into drinking.
\item[77.] That guy always says things that succeed in annoying me.
\item[78.] If someone says Egypt, we immediately call to mind the pyramids.
\item[79.] It is entirely possible that the Japanese race crossed over from the south in this way.(The theory that the Japanese race crossed over from the south in this way is entirely plausible.)
\item[80.] When I called my friend's house, a total stranger answered the phone.
\item[81.] Although this question was easy, not a single person was able to answer it.
\item[82.] Without having to think, ``I wonder what that was,'' I knew right away that the child's balloon had popped.
\item[83.] It's terribly unfortunate that that person passed away at the age of 35, in the prime of his/her working years.
\item[84.] Suzuki-san took leave of this world before his/her time, at the age of 45, and went to his/her eternal rest.
\item[85.] If I could spare the time and/or the money, I'd like to go on a trip or something, but reality is not that kind.
\item[86.] During my four years at university, I abandoned myself to pachinko and mahjong, and never studied seriously.
\item[87.] That person has already experienced that kind of thing, so he/she won't make the same mistake twice.
\item[88.] I caused my parents a great deal of worry because of this incident.
\item[89.] Knowing him, he has no common sense, so he might do such a thing.
\item[90.] From the lotus blossom emanated a fragrance so pleasant that it was beyond description.
\item[91.] Although I'd been planning on watching the 9 o'clock news, I got absorbed in my book and forgot all about it.
\item[92.] Although he/she had been fooling around every day up till then, all of a sudden he/she started studying seriously, and it was as if he/she had turned into a completely different person.
\item[93.] Because my father is an alcoholic, he can't go even a short time without a drink.
\item[94.] These days it's rare to see a whole family sit down together for a meal.
\item[95.] According to statistics, no more than 8% of all families sit down together for meals.
\item[96.] Today is Sunday, but it's raining and I don't have any money, so I have no alternative but to stay at home and sleep.
\item[97.] He couldn't possibly be a foreigner.
\item[98.] As might be expected of a student in the vocal music program, his/her speaking voice is pleasant too.
\item[99.] Because it's your fault, I think that you should apologize.
\item[100.] I don't even have a 10-yen coin, let alone a thousand-yen bill, so I can't possibly pay the money back.
\fi
\ifVOLTWO
\item[101.] It would be impossible to go out in such a fierce snowstorm, even if I tried.
\item[102.] Even if I complained to the likes of a [company] president such as him/her, he/she wouldn't listen.
\item[103.] He/she sent us one letter, and we haven't heard a word from him/her since.
\item[104.] It's a waste to leave this room unused.
\item[105.] His death will be mourned all the more deeply because he was the only painter born during the Meiji era.
\item[106.] My carelessness caused a child to be seriously injured.  (My carelessness inflicted serious injury on a child.)
\item[107.] Even though he had caught a cold, he came in first in the [long-distance] race.
\item[108.] If you're going to visit him/her in the hospital, wait until he/she gets a little better.
\item[109.]  Since then, nuclear power has come to attract attention as a new [form of] energy.
\item[110.] I almost left my umbrella on the train, you know.
\item[111.] I had a terrible time making up my mind whether to have soba (buckwheat noodles) or udon (wheat noodles), and I finally ended up having curry and rice.
\item[112.] On a hot summer day, nothing could be better than drinking cold beer in a beer garden.
\item[113.] Just what effect did these scientific-cultural phenomena have on human beings?
\item[114.] Whether you go or not, it doesn't matter to me.  (Whether you go or not has nothing to do with me.)
\item[115.] The bus is ready and waiting to leave, except that Yamada-san isn't here yet.
\item[116.] He turned to me with an expression verging on anger and said, "What brought you here?"
\item[117.] Even if the sky is cloudy, it isn't [bad] enough for you to take an umbrella with you.
\item[118.] I didn't marry Kyoko because I wanted her inheritance or anything.
\item[119.] A ``Thank you very much.  This is a gift to show my appreciation...''\\B ``That's really not necessary.''(=``Such a gift isn't at all necessary.'')\\A ``Then, could you at least tell me your name, please?''
\item[120.] The lost boy burst into tears the instant he saw his mother, who had come to pick him up.
\item[121.] I ran as hard as I could so as not to miss the train, and I made it.
\item[122.] You're not a child [anymore], and you can't go on eating kiddie lunches forever.
\item[123.] Although I'm studying very hard, my grades aren't improving the way they should.
\item[124.] I have an entrance examination tomorrow, so I don't think I'll get much sleep tonight.
\item[125.] That person appears to have already finished his meal and is having a cigarette with his coffee.
\item[126.] The opinion of the minority should be valued, but in the real world it tends to get ignored.
\item[127.] Now, at that dealer's, you can buy a Benz for 360,000 yen.  Of course, though, it doesn't have an engine.
\item[128.] Not only human societies but even monkey societies have a hierarchy of their own.
\item[129.] It would be hard enough to finish this job in three days, so telling us to finish it in half a day is absolutely crazy.
\item[130.] That person has such a look on his face, but it's not by any means because he's angry.  He always looks as if he's in a bad temper.
\item[131.] Believe it or not, this boy can read a book with more than three hundred pages in three minutes and then explain its contents!
\item[132.] After I was so kind to him/her, he/she could at least have said thank you.
\item[133.] Wouldn't it be a bit difficult to polish off three steaks and three plates of rice in an hour?
\item[134.] He is an idiot who can't be helped.
\item[135.] A ``You saved my daughter's life(=My daughter owe you her life.). I wouldn't feel right if I didn't do something to thank you.''\\B ``Oh, no, please don't bother.''
\item[136.] In your everyday life, you should refrain from behaviour that might invite misunderstanding.
\item[137.] The brothers' unseemly dispute over the inheritance continues.
\item[138.] Even if what you're saying is true, violence is wrong.
\item[139.] I hear that his illness is already past the point of curability, but let's pretend we don't know.
\item[140.] It isn't good for parents to butt in on children's quarrels.
\item[141.] It seems that autumn typhoons are frequently accompanied by heavy rain.
\item[142.] If he wants to cry, just let him cry.  He'll probably cry himself out in a little while.
\item[143.] For now, I'll just pay you 3,000 yen.  Please wait until the end of the month for the rest.
\item[144.] Some shops are friendly to customers, while others treat them coldly.
\item[145.] You know, if you scold a crying child thoughtlessly and excessively, it's not effective.
\item[146.] We'd rather buy a house than have to pay such high rent.
\item[147.] With the [signal] ``Ready, go!'' all of the competitors started off at once.
\item[148.] It is also conceivable that he stole it, but I don't want to think so.
\item[149.] Sorry to trouble you (=This may be a rather abrupt question), but could you tell me whether there is a public lavatory near here?
\item[150.] Examinations will be given class by class.
\item[151.] A child suddenly dashed out into the road, and I almost ran over and killed him/her.
\item[152.] It's not worth doing, at such a high risk.
\item[153.] Stop [your] dawdling, and hurry up and go to school.
\item[154.] Who do you want to tell this wonderful news to, first of all?
\item[155.] I'd like to continue with this work, even if it results in a big loss.
\item[156.] Whether you go on a trip or start a business of your own, spend this money on whatever you like.
\item[157.] Since I've already done this much to prepare, now I have no choice but to carry it out.
\item[158.] I've been very kind to him, but on top of that he even has the nerve to ask me for money...I'm at a loss for words.
\item[159.] Even though he/she is always borrowing money from me, he/she says, "Mum, what would you like for a present?"--which of course he/she doesn't really mean. 
\item[160.] I had thought that person was respected by everyone, but now I know I misjudged him/her completely.  What an awful thing he/she did!
\item[161.] This product is on offer at a bargain price, made possible only by direct delivery from the producer.
\item[162.] This is an ideal reference book for exam preparation.
\item[163.] Since he is trying so desperately to tell his story, it can't all be a pack of lies.
\item[164.] You've worked so hard up till now, and now you're going to quit?  Don't be silly!
\item[165.] Even if it's "all-you-can-eat," you'll probably only be able to finish up three plates at the very most, no matter how much you eat.
\item[166.] If goods are priced too highly, they won't sell well.
\item[167.] There's such a big difference of opinion between us that it's not even worth mentioning.
\item[168.] No matter how hard I try, I'll end up being called names.
\item[169.] Because nobody was kind enough to do it for me, I had no choice but to do it myself.
\item[170.] It seems that the project isn't proceeding according to plan because of insufficient funds, and because of outside interference as well.
\item[171.] When all is said and done, in the end you can trust only yourself.
\item[172.] I'm not really sure, but I think the conversation was something about the question of pensions...
\item[173.] I can tell you, it was so hugely amusing that I almost died laughing.
\item[174.] I hear they were discussing so important a matter alone together, in whispers!
\item[175.] This politician's scheme met with the criticism of the opposition parties and, furthermore, provoked the antipathy of the entire nation.
\item[176.] Cancer is not the sort of illness which people catch all of a sudden; it's a complicated and incurable disease which gnaws away day by day at the health of the patient.
\item[177.] In winter, this place is a lonesome and deserted town, but in the summer, when the swimming season opens, it livens up with young people in colourful swimsuits.
\item[178.] At Hyde Park in England, strangers engage each other in lively discussions every day.
\item[179.] The whole mountain turned into a sea of fire, all because of the tiny flame of a cigarette.
\item[180.] A wooden house, for instance, is reduced to ashes in an instant once it catches fire.
\item[181.] Certainly I'd heard it was awful, but I really didn't expect it to be this horrendous.
\item[182.] Although I did it because I thought it was a good thing to do, it ended up making that person all the more unhappy.
\item[183.] For the next test, I'm just going to write down whatever any old book says and fake my way through.
\item[184.] There are more and more suicides among the children of parents who expect too much of them.
\item[185.] This cafe has many customers who come to savour not only the smell of its coffee but also the atmosphere of the place.
\item[186.] It was not until our baby was born that I actually started to feel like a father (=that the actual feeling of being a father welled up in me).
\item[187.] It's not that I don't cook at all, but when I'm alone it's a nuisance so I usually eat out.
\item[188.] I hear that person has gone to Tokyo and doesn't live here any more.
\item[189.] He came into my room silently, without even being invited.
\item[190.] Purely and simply because I studied very hard, I was able to get a good grade.
\item[191.] What with all the surprise and rejoicing, the place was in an uproar.
\item[192.] I can't get things sorted out unless I deal with them one at a time.
\item[193.] I can't figure out what's going on.  That person turned up with a year-end gift ("oseibo")!
\item[194.] When you grow up, you must not become the kind of person who causes nuisance to others, even by mistake.
\item[195.] That person is no prime minister, after he/she went so far as to embezzle public money.
\item[196.] Carried away by her sorrow, she couldn't even cry; she just squatted down without any expression on her face.
\item[197.] [The government] lowered income taxes, but meanwhile it raised the consumption tax, in order to guarantee its financial resources.
\item[198.] Now that things have come to this, we have no choice but to do a drastic restructuring and reorganize management.
\item[199.] I put a half-finished cup of coffee beside the computer while I was working, but I accidentally spilled it.
\item[200.] It's hard to believe that they can hunt down criminals by means of extrasensory perception.
\fi
\ifVOLTHREE
\item[201.] Making nothing of the cold, he went out in thin clothes.
\item[202.] The record of hundred wins would be merely a passing point for the player(pitcher).
\item[203.] It is a prejudice of the old to think that the language of the young is poor, and vogue-words are insignificant.
\item[204.] There is an opinion which we can always make a better product if we spend more money, but we don't agree with this.
\item[205.] The sculptor said that he had never had any perfect works which could satisfy him.
\item[206.] The shop is so tiny that it becomes impossible to move with only five people inside the shop.
\item[207.] His death was a tragedy happened just as he was about to take action after saying, ``who else would do it, if I don't.''
\item[208.] The player believed that he knew everything about the world of professional baseball, but he didn't realise the existence of the people supporting players behind the scenes.
\item[209.] Many people disposed garbage that contains dangerous and unacceptable goods taking advantage of black garbage bags that do not show their contents.
\item[210.] In spite of the voices appealing for the preservation of Hiroshima Peace Memorial as a world heritage, the landmark conveying the history of Hiroshima was about to be vanished.
\item[211.] It was a heavy rain but not a serious one. However we judge that it caused floods in the various places due to its short duration.
\item[212.] S/he finished a work up by drawing and erasing it again and again. After many repeats of writing and deleting, s/he completed the work.
\item[213.] I feel abandoned and try to drink up a 1.8-litter-bottle of sake, but I have had a lot of it yet even if I keep drinking since I don't usually drink.
\item[214.] Even though he should speak his mind, he is still hesitating about doing so.
\item[215.] He became angry since someone woke him up while he was sound asleep, exhausted.
\item[216.] These two writers are the novelists unmistakably appropriate to call the competent and influential. 
\item[217.] The three children wrote the pleasant memories of the year one by one in their diaries.
\item[218.] This sumo tournament has started with eventful episodes such as both of two Yokozunas being defeated one after the other on the first day.
\item[219.] After having conducted the experiments several times, it was found that although it could be ignited, the flame would  go out immediately.
\item[220.] What we should do in future will be discussed based on the bill which was legislated recently.
\item[221.] I was just drinking beer at home without realising that such a terrible thing happened.
\item[222.] I went onto a flight right away, feeling restless, when I heard of my father's accident.
\item[223.] I think that it is very difficult, but don't give up and go for it! You have nothing to lose.
\item[224.] I think it is quite good but because it is an expensive item, I'd better ask my wife whether it is okay for me to buy it.
\item[225.] I won't be easily cheated by such a childish trick.
\item[226.] I was watching the historic moment on TV with bated breath.
\item[227.] It may have been impolite, but I could not help laughing because the design of her swimwear was very old-fashioned.
\item[228.] I have too much on my plate already.I can't do anything else for others.
\item[229.] It is good that children are delighted, but they frolic too much that makes you wonder.
\item[230.] Tonight there will be a long waited game of IAAF(International Association of Athletics Federations), for the first time in Japan, and I am very excited about it.
\item[231.] It depends on circumstances whether it is proper or not.
\item[232.] He has a good eye for arts.
\item[233.] What physicists have been trying to unveil is, to tell the truth,  nothing else but something about this natural world where we live as a matter of course.
\item[234.] A politician who said last week ``I will make the politics of Japan better'' has been arrested today due to a corruption case.
\item[235.] ``About one person is so demanding that I did what she requested unwillingly.'' ``Do yo mean it's me?''
\item[236.] Looking at a wedding as an outsider, it seems a full of happiness, but for the couple themselves it is indeed a very troublesome event.
\item[237.] He is not at all such a weak person who would whinge in the presence of other people.
\item[238.] Saving the face of their Prime Minister cannot be the purpose of the politics of any country.
\item[239.] We feel a little awkward because we have just had our wedding ceremony but let us inform you that yesterday we found out that my wife is pregnant.
\item[240.] Yesterday, I ran into my dear friend at a most unexpected place.
\item[241.] My company went bankrupt, I got into a large debt, I got a divorce, I did't know what I to do, and I was at a loss.
\fi